\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-07-13 paper/main.tex
.
Fixed TODOs with suitable citations

%\todo[inline]{Why is having only having 20\% of drugs reasonable -> significance test in results}
One major component of our experiments was to determine how the
information that is available to a machine learning model during
training affects the performance of the model. Similarly to previous
work \cite{MolTrans2020, DeepConvDTI2019}\todo{These seem wrong, they
  only use a single splitting scheme -- should this be cite:DTI-CDF2019?}, we find significant
differences in predictive performance across different splitting
schemes.

@@

Several of the biases we identify in evaluating DTI prediction methods
have been observed previously. The performance difference based on how
training and evaluation data is split (by interaction pair, by drug,
or by protein) has been demonstrated before using a
\todo{MacroAUC/MicroAUC???} measure \cite{}; we further extend on
these results by introducing performance measures based on micro
averages (Micro AUC$_p$ and Micro AUC$_d$) to further illustrate how
prediction performance changes when evaluation data is imbalanced. We
have further extended on prior results by introducing a ``na\"ive''
classifier that explicitly exploits one data bias to make predictions,
illustrating that this bias has a significant impact on DTI
methods. The bias we identify with the ``na\"ive'' classifier is
similar to a previous bias found in gene networks when using methods
that rely on the guilt-by-association principle
\cite{Gillis2012} but which has, to our knowledge,
not been demonstrated in the context of DTI prediction.

>>>>

%\todo[inline]{Why is having only having 20\% of drugs reasonable -> significance test in results}
One major component of our experiments was to determine how the
information that is available to a machine learning model during
training affects the performance of the model. Similarly to previous
work \cite{MolTrans2020, DeepConvDTI2019, DTI-CDF2019}, we find significant
differences in predictive performance across different splitting
schemes.

@@

Several of the biases we identify in evaluating DTI prediction methods
have been observed previously. The performance difference based on how
training and evaluation data is split (by interaction pair, by drug,
or by protein) has been demonstrated before using the MacroAUC measure \cite{MolTrans2020, Pahikkala2014, vanLaarhoven2014}; we further extend on
these results by introducing performance measures based on micro
averages (Micro AUC$_p$ and Micro AUC$_d$) to further illustrate how
prediction performance changes when evaluation data is imbalanced. We
have further extended on prior results by introducing a ``na\"ive''
classifier that explicitly exploits one data bias to make predictions,
illustrating that this bias has a significant impact on DTI
methods. The bias we identify with the ``na\"ive'' classifier is
similar to a previous bias found in gene networks when using methods
that rely on the guilt-by-association principle
\cite{Gillis2012} but which has, to our knowledge,
not been demonstrated in the context of DTI prediction.
